outline!

### 2016-05-19 paper.tex
paper: update
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

To illustrate this we ran the same benchmark that measures expected append
throughput shown in Figure~\ref{fig:vanilla_wr_jewel} on identical hardware
but with a version of long-term support version of Ceph released two years
ago. The result of this benchmark is shown in Figure~\ref{fig:vanilla_wr_firefly}
in which the bytestream interface outperforms the key-value interface by 12\%,
compared to over 100\% in the newer versino of Ceph. Qualatatively, given the
reduced overall throughput achieved in the older version, some developers may
find that incurring the overhead of using the key-value interface is an easy
decision given the reduced complexity of the design space for metadata
management.

>>>>

To illustrate this we ran the same benchmark that measures expected append
throughput shown in Figure~\ref{fig:vanilla_wr_jewel} on identical hardware
but we used a long-term support version of Ceph released two years
ago. The result of this benchmark is shown in Figure~\ref{fig:vanilla_wr_firefly}
in which the bytestream interface outperforms the key-value interface by 12\%,
compared to over 100\% in the newer versino of Ceph. Qualatatively, given the
reduced overall throughput achieved in the older version, some developers may
find that incurring the overhead of using the key-value interface is an easy
decision given the reduced complexity of the design space for metadata
management. If this choice had been made, then a future system upgrade could
drop a significant number of iops on the floor.
